# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r}
if (!file.exists("activity.csv")) {
  download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",  method="curl", destfile="repdata_data_activity.zip");
  unzip("repdata_data_activity.zip");
}

activity = read.csv("activity.csv");
activity = activity[complete.cases(activity),];
```

## What is mean total number of steps taken per day?

```{r}
dailyMeans = tapply(activity$steps,INDEX=activity$date, FUN=mean);
hist(dailyMeans);
```
  
Please see mean of total number of steps taken per day:

```{r}
print(mean(dailyMeans, na.rm=T));
```

  
Please see median of total number of steps taken per day:
```{r}
print(median(dailyMeans, na.rm=T));
```


## What is the average daily activity pattern?

```{r}
patterns = tapply(activity$steps, INDEX=activity$interval, FUN=mean);
plot(patterns, type="l")
```

  
Maximum interval value was:
```{r}
print(maximum(pattern));
```

  
For an interval:
```{r}
print(names(patterns)[match(maximum(pattern))]);
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
